Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
methods: honing & typos (v1)

\begin{itemize}
    \item main text: add references to supplemental material
\end{itemize}

@@

% intro
We used three components of the publicly available
\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already
been used by other research groups in independent studies (e.g.
\citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AD
a) listening to the audio-description (AD study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'',
% AV
b) watching the original movie (AV study; \citep{hanke2016simultaneous}), and
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}).
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

% AD & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
broadcast as an additional audio track for visually impaired listeners on Swiss
public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AD: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

% AD & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes, less relevant to the main plot, were removed to create
the ``research cut'' lasting \unit[$\approx$2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning.
% splitting
Each stimulus was split into eight segments of approximately \unit[15]{minutes}.
% AD & AV: instructions
Before the experiment, participants were instructed to inhibit physical
movements except for eye-movements, and otherwise to simply ``enjoy''.
% AD & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}.
%
There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% traditionally
Traditionally, researchers specifically design stimuli that presumably would
trigger the perceptual process of interest while also controlling confounding
variables (e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli mimic how we experience the world more closely but have the
drawback that they are usually fix and that their temporal structure is unknown.
% annotation ftw
Hence, we annotated the temporal structure of a various stimulus features that
later served as a basis (for GLM regressors) to model hemodynamic responses.

% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of [the 869] movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either changing the perspective
within a setting or switching to another setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale (e.g. room) that
was depicted for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% AV COPEs: intro
The rationale that this approach would yield categories that - on average - show
different stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Later in the movie when the spatial layout of a setting is already established,
shots within a setting shift to objects more relevant to the evolved plot and or
to switching between faces of persons talking to each others (\texttt{vpe\_old})
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.
%
\todo{drop last sentence \& better focus on cinematographic rationale; activity
in e.g. FFA adopts too -> we might subtract an on average smaller response}
% no cut condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

>>>>

\begin{itemize}
    \item main text: add references to supplemental material
    \item imo AD and AV can be written as movie and audio-description
    \item [text in brackets] can probably be deleted
\end{itemize}

@@

% intro
We used three components of the publicly available
\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already
been used by other research groups in independent studies (e.g.
\citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AD
a) listening to the audio-description \citep{hanke2014audiomovie} of
the movie ``Forrest Gump'',
% AV
b) watching the audio-visual movie \citep{hanke2016simultaneous}, and
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS; \citep{sengupta2016extension}).
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

% AD & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie} and its audio-description that was broadcast as
an additional audio track for visually impaired listeners on Swiss public
television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AD: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

% AD & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes, less relevant to the main plot, were removed to create
the ``research cut'' lasting \unit[$\approx$2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning.
% splitting
Each stimulus was split into eight segments of approximately \unit[15]{minutes}.
% AD & AV: instructions
Before the experiment, participants were instructed to inhibit physical
movements except for eye-movements, and otherwise to simply ``enjoy'' the
stimulus.
% AD & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}.
%
There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}.
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% traditionally
Traditionally, researchers design stimuli that presumably would trigger the
perceptual process of interest while also controlling confounding variables
(e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli mimic how we experience the world more closely but have the
drawback that they are usually fix and that their temporal structure is unknown.
% annotation ftw
Hence, we annotated the temporal structure of various stimulus features that
later served as basis [for GLM regressors] to model hemodynamic responses.

% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of [the 869] movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either switching to another
setting or switching the perspective within the same setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% assumption
We assumed that different categories would - on average - depict different
stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial layout within a setting (\texttt{vpe\_new})
at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to an already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
When the spatial layout within a setting is already established, shots tend to
more often depict (faces of) persons talking to each others or objects more
relevant to the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
mercado2011filmmakers}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{hausler2021studyforrest} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.
